\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-09-07 Paper/Paper.tex
small revision
add front page

\begin{document}
	\title{\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis}
	\author{Siqi Pan}
	\date{}
	\maketitle

@@

	\vspace{-0.5cm}
	\begin{minipage}[t]{0.4\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccc}
					\caption{Data sources of OCT abnormities}
					\label{tb:OCT_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&\\
					\midrule
					CNV    &2984&-  &- &- &2984\\
					CSC    &-   &102&32&- &134 \\
					DME    &2500&-  &- &- &2500\\
					Drusen &2500&-  &- &- &2500\\
					ERM    &-   &-  &- &16&16  \\
					IF     &1097&-  &- &- &1097\\
					MH     &-   &99 &31&- &130 \\
					Mactel &-   &-  &29&- &29  \\
					Healthy&5000&-  &- &- &5000\\
					RP     &-   &102&31&- &133 \\
					ST     &-   &-  &23&- &23  \\
					SF     &1083&-  &- &- &1083\\
					\bottomrule
				\end{longtable}

@@

				\vspace{0.5cm}
			}
		}
	\end{minipage}
	\begin{minipage}[t]{0.6\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccccc}
					\caption{Data sources of fundus abnormities}
					\label{tb:Fundus_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{6}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&5&6&\\
					\midrule
					CWP    &-  &- &- &33 &205&- &238\\
					Drusen &-  &- &- &50 &-  &- &50 \\     
					HE     &20 &- &- &75 &284&- &379\\ 
					HM     &13 &66&- &105&278&- &462\\     
					MH     &-  &- &- &-  &-  &34&34 \\        
					MA     &55 &- &- &1  &219&- &275\\
					Healthy&100&37&15&-  &-  &- &152\\      
					RP     &-  &22&- &-  &-  &44&66 \\         
					VA     &-  &64&- &14 &-  &- &78 \\

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.pdf}
		\caption{GradCAM highlighting of multiple abnormities}
		\vspace{0.3cm}
		\label{fig:gradCAM_multi_abnormity}
	\end{figure}

>>>>

\begin{document}
	\vspace{5cm}

	{\fontsize{20pt}{20pt}\selectfont 参赛学生姓名： 潘思齐\\}

	\vspace{0.6cm}
	{\fontsize{20pt}{20pt}\selectfont 中学： 上海市世外中学}

	\vspace{1cm}
	{\fontsize{20pt}{20pt}\selectfont 省份： 上海}

	\vspace{1cm}
	{\fontsize{20pt}{20pt}\selectfont 国家/地区： 中国}

	\vspace{1cm}
	{\fontsize{20pt}{20pt}\selectfont 指导老师姓名： 徐庆林}

	\vspace{1cm}
	{\fontsize{20pt}{20pt}\selectfont 指导老师单位： 上海市世外中学}

	\vspace{1cm}
	{\fontsize{20pt}{20pt}\selectfont 论文题目： }
	{\fontsize{16pt}{16pt}\selectfont Multimodal Abnormity-Aware Model}

	\vspace{0.2cm}
	{\fontsize{16pt}{16pt}\selectfont \hspace{3.7cm} for Ocular Disease Diagnosis}

	\title{\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis}
	\author{Siqi Pan}
	\date{}
	\maketitle

@@

	\vspace{-0.5cm}
	\begin{minipage}[t]{0.4\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccc}
					\caption{OCT Data sources}
					\label{tb:OCT_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&\\
					\midrule
					CNV    &2984&-  &- &- &2984\\
					CSC    &-   &102&32&- &134 \\
					DME    &2500&-  &- &- &2500\\
					Drusen &2500&-  &- &- &2500\\
					ERM    &-   &-  &- &16&16  \\
					IF     &1097&-  &- &- &1097\\
					MH     &-   &99 &31&- &130 \\
					Mactel &-   &-  &29&- &29  \\
					Healthy&5000&-  &- &- &5000\\
					RP     &-   &102&31&- &133 \\
					ST     &-   &-  &23&- &23  \\
					SF     &1083&-  &- &- &1083\\
					\bottomrule
				\end{longtable}

@@

				\vspace{0.5cm}
			}
		}
	\end{minipage}
	\begin{minipage}[t]{0.6\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccccc}
					\caption{Fundus Data sources}
					\label{tb:Fundus_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{6}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&5&6&\\
					\midrule
					CWP    &-  &- &- &33 &205&- &238\\
					Drusen &-  &- &- &50 &-  &- &50 \\     
					HE     &20 &- &- &75 &284&- &379\\ 
					HM     &13 &66&- &105&278&- &462\\     
					MH     &-  &- &- &-  &-  &34&34 \\        
					MA     &55 &- &- &1  &219&- &275\\
					Healthy&100&37&15&-  &-  &- &152\\      
					RP     &-  &22&- &-  &-  &44&66 \\         
					VA     &-  &64&- &14 &-  &- &78 \\

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.pdf}
		\caption{Grad-CAM highlighting of multiple abnormities}
		\vspace{0.3cm}
		\label{fig:gradCAM_multi_abnormity}
	\end{figure}
